Recipient plant traits are important determinants of the impacts of heterospecific pollen upon plant reproduction

### 2019-03-17 Manuscript_draft/Tables_and_figures.Rmd
change in figure

p2 <- ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="B) Solanaceae") +
  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")

p3 <-ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="C) Convolvulaceae") +
  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
grid.arrange(p1, p3,p2, nrow = 3, ncol=1)

@@

p2 <- ggplot(total_pollen_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="B) Solanaceae") +
  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor"))+ xlab("") + ylab("Total pollen")

p3 <-ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="C) Convolvulaceae") +
  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor"))+ xlab("") + ylab("Total pollen")
grid.arrange(p1, p3,p2, nrow = 3, ncol=1)

@@

**Table 3** Seed production for the treatments that produced seeds with 100% foeign pollen.

>>>>

p2 <- ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="C) Solanaceae") +
  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")

p3 <-ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="B) Convolvulaceae") +
  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
grid.arrange(p1, p3,p2, nrow = 3, ncol=1)

@@

p2 <- ggplot(total_pollen_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="C) Solanaceae") +
  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor"))+ xlab("") + ylab("Total pollen")

p3 <-ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="B) Convolvulaceae") +
  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor"))+ xlab("") + ylab("Total pollen")
grid.arrange(p1, p3,p2, nrow = 3, ncol=1)

@@

**Table 3** Seed production for the treatments that produced seeds with 100% foreign pollen.
